SunPy - Python for Solar Physics

### 2014-01-28 1-Introduction.tex
a few minor changes to Intro.

SunPy aims to provide a free, open-source and openly developed software package 
for the analysis and visualisation of solar data. SunPy makes use of the Python 
programming language and the breadth of high-quality science-focused packages 
written in that language. Python is a general-purpose, 
powerful and easy-to-learn high-level programming language.
According to the 
2014 TIOBE Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
 Python is one of the top ten most popular programming languages in the world 
and is widely used outside of scientific fields in areas like web development, education 
and `big data' analytics.

The development of a package such as SunPy in Python is made possible by the 
rich ecosystem of scientific packages available in Python. Core packages in this 
ecosystem such as \texttt{NumPy}, \texttt{SciPy} and \texttt{matplotlib} 
provide the basic functionality expected of a scientific programming language -- 
\textit{e.g.}, array manipulation, core numerical algorithms and visualisation. 
Built upon these foundations, packages such as \texttt{Astropy}, \texttt{pandas} and 
\texttt{scikit-image} provide more domain-specific functionality.

>>>>

SunPy aims to provide a free, open-source and openly developed software package 
for the analysis and visualisation of solar data. SunPy makes use of the Python 
programming language and the breadth of high-quality science-focused packages 
written in that language. Python is a general-purpose, 
powerful and easy-to-learn high-level programming language.
According to the 
2014 TIOBE Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
 it is one of the top ten most popular programming languages in the world 
and is widely used outside of scientific fields in areas like web development, education 
and `big data' analytics.

The development of a package such as SunPy in Python is made possible by the 
rich ecosystem of scientific packages available in Python. Core packages such as \texttt{NumPy}, \texttt{SciPy} and \texttt{matplotlib} 
provide the basic functionality expected of a scientific programming language,
\textit{e.g.}, array manipulation, core numerical algorithms and visualisation. 
Building upon these foundations, packages such as \texttt{Astropy}, \texttt{pandas} and 
\texttt{scikit-image} provide more domain-specific functionality.
